The design flaw of npm and how `everything' broke it

### 2024-02-26 Paper/2/Paper.tex
More work, 4 pages is so long

\subsection{Historic Related Incidents}
npm was not a strange to packages and projects before `everything'.

@@

\subsubsection{hoarders}
was a package that was created near the early conception of npm (2012) that also depended
on 11,000 packages at its inception \cite{github-hoarders-dependencies}. Isaac Schluter (
the founder of npm) talked with the creator of the package and convinced him to unpublish it
\cite{github-hoarders}.  A few years later in Aug 19, 2021

>>>>

\subsection{Historic Related Incidents}
npm was not a stranger to packages and projects before `everything'.

@@

\subsubsection{hoarders}
was a package created by Josh Holbrook that was created near the conception of npm (2012) that
also depended on 11,000 packages at its inception \cite{github-hoarders-dependencies}.
Isaac Schluter (the founder of npm) talked with the creator of the package and convinced
him to unpublish it \cite{github-hoarders}.  A few years later in Aug 19, 2021, Josh Holbrook
found a way to work around having a heavy load on npm.

`now, rather than installing the utilities as direct dependencies, hoarders
installs them lazily, on-the-fly. this change is practically seamless - simply
reach for the utility like you would normally and hoarders will do the rest! the
only requirements are npm and an internet connection.' \cite{github-hoarders}

\subsection{Response}
PatrickJS and Evan Boehs weren't aware of the consequences of their actions
until they realized that they had broken the npm registry
\cite{youtube-everything}. They reached out to npm and created an issue on the
GitHub repository documenting and explaining the issue
\cite{bleepingcomputer-everything}.

\section{Microsoft's Response}
